### 2014-04-11 brains-protocol.tex
Clean up some comments

\begin{itemize}
    \item \textbf{Word frequency}: the frequency at which words appear in our dataset, \rk{add ref saying it's important}
    \item \textbf{Age of Acquisition}: the average age at which words are learned, obtained from~\citet{kuperman12},
    \item The average \textbf{Number of Phonemes} for all pronunciations of a word, obtained from the Carnegie Mellon University Pronouncing Dictionary~\citep{Weide98},\footnote{The CMU Pronouncing Dictionary is included in the NTLK package~\citep{Bird09}, the natural language processing toolkit we used for the analysis.}
    \item The average \textbf{Number of Syllables} for all pronunciations of a word, also obtained from the CMU Pronouncing Dictionary,
    \item The \textbf{Number of Meanings} for a word, obtained from WordNet~\citep{WordNet10}. \rk{add ref on why it's important}
\end{itemize}

@@

\begin{figure}[!th]
    \centering
    \includegraphics[width=\linewidth]{images/computed-figures/feature_correlations-filter1.png}
    \caption{Correlations in the initial set of features \rk{show non log version?}}
    \label{fig:feature-corrs-initial}
\end{figure}

Age of acquisition is a key variable which appears as a usual suspect in psycholinguistic studies and is also usually correlated to many of the other variables.
This relates to an ongoing debate suggesting that age of acquisition encodes a variety of phenomena, difficult to disentangle from more specific phenomena which could be captured by more independent variables such as~\CN{}.
Here however, as can be seen in Figure~\ref{fig:feature-corrs-initial}, age of acquisition has a relatively low correlation to the other variables (absolute value not above $0.42$ if we exclude the centrality measures), leading us to keep the variable in the rest of the analysis.

@@

\begin{figure}[!th]
    \centering
    \includegraphics[width=0.788\linewidth]{images/computed-figures/feature_correlations-filter2.png}
    \caption{Correlations in the filtered set of features \rk{show non log version?}}
    \label{fig:feature-corrs-filtered}
\end{figure}

@@

\rk{on pourrait en fait modéliser et formaliser ça de façon bien poussée en allant chercher du côté de l'analyse des séries temporelles et des processus stochastiques en général, mais bon...
c'est pas le but ici, et ça serait une toute autre recherche, et un autre public.
Oder?}

>>>>

\begin{itemize}
    \item \textbf{Word frequency}: the frequency at which words appear in our dataset, \rk{add ref on why it's important}
    \item \textbf{Age of Acquisition}: the average age at which words are learned, obtained from~\citet{kuperman12},
    \item The average \textbf{Number of Phonemes} for all pronunciations of a word, obtained from the Carnegie Mellon University Pronouncing Dictionary~\citep{Weide98},\footnote{The CMU Pronouncing Dictionary is included in the NTLK package~\citep{Bird09}, the natural language processing toolkit we used for the analysis.}
    \item The average \textbf{Number of Syllables} for all pronunciations of a word, also obtained from the CMU Pronouncing Dictionary,
    \item The \textbf{Number of Meanings} for a word, obtained from WordNet~\citep{WordNet10}. \rk{add ref on why it's important}
\end{itemize}

@@

\begin{figure}[!th]
    \centering
    \includegraphics[width=\linewidth]{images/computed-figures/feature_correlations-filter1.png}
    \caption{Correlations in the initial set of features \rk{show non-log version?}}
    \label{fig:feature-corrs-initial}
\end{figure}

Age of acquisition is a key variable which appears as a usual suspect in psycholinguistic studies and is also usually correlated to many of the other variables.
This relates to an ongoing debate suggesting that age of acquisition encodes a variety of phenomena, difficult to disentangle from more specific phenomena which could be captured by more independent variables~\CN{}.
Here however, as can be seen in Figure~\ref{fig:feature-corrs-initial}, age of acquisition has a relatively low correlation to the other variables (absolute value not above $0.42$ if we exclude the centrality measures), leading us to keep the variable in the rest of the analysis.

@@

\begin{figure}[!th]
    \centering
    \includegraphics[width=0.788\linewidth]{images/computed-figures/feature_correlations-filter2.png}
    \caption{Correlations in the filtered set of features \rk{show non-log version?}}
    \label{fig:feature-corrs-filtered}
\end{figure}

@@
